% Shared CV body content. Single source of truth.
% Do not compile this file directly. Edit here; all modes pick it up.
% Visibility: always (core) | \ifcvmedium (short+full) | \ifcvextended (full only)

\raggedright{}

\begin{center}\namefont{\myname}\end{center}

\ifcvextended
  \vspace{1em}
\else\ifcvmedium
  \vspace{0.6em}
\else
  \vspace{0.35em}
\fi\fi
\begin{minipage}[t]{0.700\textwidth}
    Organizations, Strategy and International Management \\
    Naveen Jindal School of Management \\
    The University of Texas at Dallas \\
    Richardson, TX 75080, USA
\end{minipage}
\begin{minipage}[t]{0.295\textwidth}
    \raggedleft
    \href{mailto:he.huang@utdallas.edu}{he.huang@utdallas.edu} \\
    +1 (469) 996-8112 \\
    \href{https://orcid.org/0000-0001-5915-5988}{ORCID: 0000-0001-5915-5988}
\end{minipage}


\section*{Education}

\begin{tablist}
    \item[Ph.D.]\tab{}Organizational Behavior and Human Resources \\The University of Texas at Dallas, 2021--present\\
    \textit{Dissertation: A Second Chance or A Second Guess? Recruiter Evaluation of Boomerang Candidates.}

    \item[B.S.] \tab{}Human Resource Management\\Wuhan University, 2020
\end{tablist}


\section*{Research Areas}

\begin{itemize}
    \item Employee Mobility: boomerang employment, hiring decisions, atypical career path
    \item Person-Environment Fit: leader-follower interaction, team member interaction, congruence effect
\end{itemize}


\section*{Publications}

\subsection*{Journal Articles}

\begin{tablist}
    % Shared rank mark: define once (fn:rank), reuse with \footref so JIBS/JAP
    % share the same footnote symbol and a single page-bottom note.
    \item[2026]\tab{}Takeuchi, R., \textbf{Huang, H.}\footref{fn:eqauth}, Zhou, Y.\footref{fn:eqauth}, Kim, H., \& Zhang, Z. \enquote{3-P Framework for Workforce Management: Commentary on Han et al.’s (2026) Meta-Analytic Work on High-Investment HR System.} \textit{Journal of International Business Studies}\footnote{\label{fn:rank}Denotes journal listed on ABDC\,A\textsuperscript{*}, ABS\,4\textsuperscript{*}, FT50, TAMUGA, and/or UTD24 (alphabetical by list).} [Conditional acceptance; peer-reviewed].

    \item[2022]\tab{}Hu, L., Jiang, N., \textbf{Huang, H.}, \& Liu, Y. \href{https://doi.org/10.1108/LODJ-06-2021-0312}{\enquote{Perceived Competence Overrides Gender Bias: Gender Roles, Affective Trust and Leader Effectiveness.}} \textit{Leadership \& Organization Development Journal}, 43(5): 719--733.
\end{tablist}


\subsection*{Best Paper Proceedings}

\begin{tablist}
    \item[2025]\tab{}\textbf{Huang, H.}, Wu, J., Jiang, N., \& Liu, Y. \href{https://journals.aom.org/doi/abs/10.5465/AMPROC.2025.60bp}{\enquote{Mutual Efforts Into Leader-Follower Relationship, Relational Energy, and Resilience.}} In Sonia Taneja (Ed.), \textit{Proceedings of the \nth{85} Annual Meeting of the Academy of Management.} Online ISSN: 2151-6561.
\end{tablist}


\subsection*{Manuscripts under Review}

\begin{tablist}
    \item[\nth{1} R\&R]\tab{}Kim, H.\footnote{\label{fn:eqauth}These authors contributed equally to this work.}, Takeuchi, R.\footref{fn:eqauth}, \textbf{Huang, H.}, \& Yun, S. \enquote{Exchange (In)congruence: Integration of Social Exchange and Person-Supervisor Fit Theories.} \textit{Journal of Applied Psychology}\footref{fn:rank}.
\end{tablist}


\ifcvextended
\subsection*{Manuscripts in Progress}

\begin{tablist}
    \item[]\tab{}\textbf{Huang, H.}, Wu, J., Jiang, N., \& Liu, Y. \enquote{Linking Mutual Efforts to Employee Resilience Through Relational Energy.} \textit{Revising stage, targeting: Human Relations}.

    \item[]\tab{}\textbf{Huang, H.}, Takeuchi, R., \& Guo, N. \enquote{Boomerang Employment and Firm Performance.} \textit{Data analysis stage}.

    \item[]\tab{}\textbf{Huang, H.} \enquote{How Do Female Entrepreneurs Use the Token to Overcome Gender Bias?} \textit{Data collection stage}.

    \item[]\tab{}Wu, J., \textbf{Huang, H.}, Gong, Y., \& Chen, L. \enquote{Do Experienced Tensions Lead to Creativity? Divergent Effects on Individual and Team Creativity.} \textit{Writing stage, targeting: Academy of Management Journal}.

    \item[]\tab{}Takeuchi, R., \textbf{Huang, H.}, Kim, H., Shao, R.,  \& Zhang, R. \enquote{High Investment Human Resource System and Cultural Values.}  \textit{Manuscript preparation stage, targeting: Academy of Management Journal}.

    \item[]\tab{}Wu, J., Zhang, Z., Liden, R.C., Song, L.J., \& \textbf{Huang, H.} \enquote{A Multilevel Examination of LMX Differentiation Congruence Effect.} \textit{Data analysis stage, targeting: Academy of Management Journal}.

    \item[]\tab{}Zhu, J., Liu, Y., Hu, L., \textbf{Huang, H.}, \& Fu, Z. \enquote{The Effects of Family Intrusiveness on Subjective Career Success and Conflict at Home: The Self-Verification Perspective.} \textit{Manuscript preparation stage}.
\end{tablist}
\fi


\ifcvmedium
\section*{Conference Participation}

\subsection*{Presentations}

\begin{tablist}
    \item[2025]\tab{}\textbf{Huang, H.} \enquote{Dissertation Chapter 3: Qualitative findings.} \textit{Academic Career Development Conference}. The University of Alabama. Tuscaloosa, AL. Sep 20.

    \item[2025]\tab{}\textbf{Huang, H.} \enquote{A Second Chance or A Second Guess? Recruiter Evaluation of Boomerang Candidates.} \textit{\nth{1} Lone Star Management Research Consortium}.  Mays Business School, Texas A\&M University. College Station, TX. Sep 12--13.

    \item[2025]\tab{}\textbf{Huang, H.}, Wu, J., Jiang, N., \& Liu, Y. \enquote{Mutual Efforts Into Leader-Follower Relationship, Relational Energy, and Resilience.} \textit{Academy of Management Annual Meeting}. Copenhagen, Denmark. Jul 28.

    \item[2025]\tab{}Wu, J., Song, L.J., \textbf{Huang, H.}, \& Zhang, A.M. \enquote{The Trickle-Down Effect of Servant Leadership Revisited: A Longitudinal Investigation.} \textit{Academy of Management Annual Meeting}. Copenhagen, Denmark. Jul 28.

    \item[2023]\tab{}\textbf{Huang, H.} \enquote{How Do Ambivalent Leaders Influence Employee Engagement?} \textit{PhD Student Poster Competition and Art Showcase}. The University of Texas at Dallas. Richardson, TX. Oct 25.

    \item[2021]\tab{}Liu, Y., \textbf{Huang, H.}, Jiang, N., \& Li, Y. \enquote{Competence-Bonus Effects for Female Leaders: Gender Roles, Affective Trust and Leader Effectiveness.} \textit{Academy of Management Annual Meeting}. Virtual.
\end{tablist}
\fi


\ifcvmedium
\section*{Teaching}

\ifcvextended
\subsection*{The University of Texas at Dallas, Instructor}

\begin{itemize}
\item Organizational Behavior (Summer 2026; Undergraduate, 54 students)
\item Human Resource Management in Business (Spring 2026; Undergraduate, 39 students)
\item Organizational Behavior (Fall 2024; Undergraduate, 62 students)
\item Organizational Behavior (Spring 2024; Undergraduate, 30 students)
\end{itemize}

\subsection*{The University of Texas at Dallas, Teaching Assistant}

\begin{itemize}
\item Strategic Leadership (Fall 2025; Executive MBA)
\item Special Topics in Entrepreneurship (Fall 2025; Graduate)
\item Negotiation and Dispute Resolution (Fall 2025, Fall 2023; Executive MBA, Graduate)
\item Strategic Management (Spring 2025; Executive MBA)
\item Introduction to Human Resource Management (Spring 2025, Fall 2022; Undergraduate)
\item Healthcare Operations Management (Summer 2024; Graduate)
\item Organizational Behavior (Fall 2023, Spring 2022; Undergraduate)
\end{itemize}
\else
% short: instructor courses only, compact lines
\begin{itemize}
\item Organizational Behavior (Summer 2026, Fall 2024, Spring 2024; Undergraduate), Instructor
\item Human Resource Management in Business (Spring 2026; Undergraduate), Instructor
\end{itemize}
\fi
\fi


\section*{Awards and Honors}

\begin{tablist}
    \item[2022--23]\tab{}Jindal Research Fellowship, The University of Texas at Dallas
\end{tablist}


\ifcvextended
\section*{Professional Development}

\subsection*{Consortium for the Advancement of Research Methods and Analysis}

\begin{tablist}
    \item[2026]\tab{}Machine Learning/Natural Language Processing
    \item[2025]\tab{}Publishing Papers with Interview Data
    \item[2023]\tab{}Alternatives to Difference Scores
    \item[2022]\tab{}Advanced SEM II
    \item[2022]\tab{}Advanced SEM I
    \item[2022]\tab{}Introduction to SEM
    \item[2021]\tab{}Systematic Reviews and Meta-Analysis in R
\end{tablist}

\subsection*{Academy of Management}

\begin{tablist}
    \item[2025]\tab{}Behind the Scenes of Highly Cited Organizational Ethnographies, PDW
    \item[2022]\tab{}New Doctoral Student Consortium
\end{tablist}

\subsection*{The University of Texas at Dallas}

\begin{tablist}
    \item[2025]\tab{}Graduate Teaching Certificate
\end{tablist}

\subsection*{Neuromatch Academy}

\begin{tablist}
    \item[2021]\tab{}Computational Neuroscience Education
\end{tablist}


\section*{Service}

\subsection*{Peer Review}

\begin{itemize}
    \item Human Resource Management
    \item Applied Psychology
    \item Career Development International
    \item Leadership \& Organization Development Journal
    \item Academy of Management Annual Conference
\end{itemize}

\subsection*{Service to the Community}

\begin{tablist}
    \item[2025]\tab{}Academy of Management Annual Meeting, Session Moderator
    \item[2023--24]\tab{}JSOM PhD Social Club, The University of Texas at Dallas, Vice President of Communications
    \item[2023--24]\tab{}OSIM PhD Student Brownbag Series, The University of Texas at Dallas, Moderator
\end{tablist}
\fi


\ifcvmedium
\section*{Society Membership}

\subsection*{Academy of Management}

\begin{itemize}
    \item Organizational Behavior Division
    \item Human Resources Division
    \item Managerial and Organizational Cognition Division
\end{itemize}

\subsection*{Society for Industrial and Organizational Psychology}

\begin{itemize}
    \item Member
\end{itemize}
\fi


\ifcvextended
\newpage

\section*{References}

\subsection*{Riki Takeuchi, Ph.D. (Dissertation Co-chair)}
\begin{minipage}[t]{0.700\textwidth}
Dr. Joseph Picken Distinguished Professor \\in Innovation and Entrepreneurship\\
Organizations, Strategy and International Management\\
Naveen Jindal School of Management\\
The University of Texas at Dallas
\end{minipage}
\begin{minipage}[t]{0.295\textwidth}
\raggedleft
\href{mailto:riki.takeuchi@utdallas.edu}{riki.takeuchi@utdallas.edu} \\
+1 (972) 883-5112 \\
800 West Campbell Road\\
Richardson, TX 75080, USA
\end{minipage}

\subsection*{Junfeng Wu, Ph.D. (Dissertation Co-chair)}
\begin{minipage}[t]{0.700\textwidth}
Associate Professor of Management \\
Organizations, Strategy and International Management \\
Naveen Jindal School of Management \\
The University of Texas at Dallas
\end{minipage}
\begin{minipage}[t]{0.295\textwidth}
\raggedleft
\href{mailto:junfeng.wu@utdallas.edu}{junfeng.wu@utdallas.edu} \\
+1 (972) 883-5053 \\
800 West Campbell Road\\
Richardson, TX 75080, USA
\end{minipage}

\subsection*{Karren Knowlton, Ph.D.}
\begin{minipage}[t]{0.700\textwidth}
Assistant Professor of Organizational Behavior\\
Organizations, Strategy and International Management\\
Naveen Jindal School of Management\\
The University of Texas at Dallas
\end{minipage}
\begin{minipage}[t]{0.295\textwidth}
\raggedleft
\href{mailto:knowlton@utdallas.edu}{knowlton@utdallas.edu} \\
+1 (972) 883-5002 \\
800 West Campbell Road\\
Richardson, TX 75080, USA
\end{minipage}
\fi


\begin{center}
   \vfill
    updated \monthyeardate\today
\end{center}
